---
title: "HW2_bdbarbe2"
author: "Beau Barber"
date: "9/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## W2 Question 2
2 - Create an R Markdown document and do the following (include the R code in all of your answers):

     a) show the step-by-step how to solve the following system of equations in R (Use R chunks to run each part). 

      2x + 5y = 33

      x + 3y = 19
      
      Step - by - Step Solution
      
      2x+5y=33
      1x+3y=19
      
      Can be written in the matrix notation
      
       x  y  = C
      [2, 5, 33;
       1, 3, 19]
       
       
       Converting to Row Reduced Echelon Form by Gaussian Jordan Elimination
       
       Multiply Row1 by 1/2
       
       [1, 2.5, 16.5;
        1, 3  , 19]
        
        Subtract Row 1 from Row 2
        
        [1, 2.5, 16.5;
         0, 0.5, 2.5]
         
         Divide Row 2 by 0.5
         
         [1 2.5 16.5;
          0 1   5   ]
          
          From this I can tell y = 5, but continuing on
          
         Subtract (Row 2)*2.5 from Row 1
         
          x y
         [1 0 4;
          0 1 5]
          
          From this we have x=4, y=5
# CHECK  

    2x+5y=33       2(4)+5(5)=33 -->  8+25=33 --> 33=33
    1x+3y=19       1(4)+3(5)=19 -->  4+15=19 --> 19=19
         
```{r}
    sys_equations <- rbind(c(2,5),c(1,3))
    print(sys_equations)
    writeLines("\n")
    rref_equations <- solve(sys_equations,c(33,19))    #solve function solve(a,b) where "a" is the equation on the left hand side (coefficients of variables) and "b" is the right hand side (solution/constants)
    print(rref_equations)
```
      

b) create a vector that goes from 1 to 100 and calculates the average of it WITHOUT using the R function “mean”.

```{r}
   num_vec <- 1:100 #Creates the vector
   #I can calculate the mean by taking the sum of the vector divided by its length
   sum_val=sum(num_vec)
   print(sum_val)
   length_val=length(num_vec)
   print(length_val)
   mean_of_vector <- sum(num_vec)/length(num_vec)
   print(mean_of_vector)
```


c) install the package “dplyr”.

```{r}
install.packages("dplyr")
require("dplyr")
```


3 - create a data frame of two rows with A, B, C, and D in row 1 and D, E, F, and G in row 2.

```{r}
df_char=data.frame(data = rbind(c("A","B","C","D"),c("D","E","F","G")))
print(df_char)
```


4 - Create a repository on your GitHub account (not in the IntroToR organization!) and push the R Markdown file created on #2.


